Supermassive black holes and host bulges affairs -- \\ II. The red and the blue sequences in the mass -- mass diagram.

### 2015-04-30 papers/MbhMsph/mm.tex
thu

@@

comes from the compilation of \citet{savorgnangraham2014},

@@

Following GS13, we assumed a fixed uncertainty ($0.25\rm~mag$) for $MAG_{\rm gal}$.

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mag_tot.pdf}
\caption{Black hole mass against $3.6\rm~\mu m$ galaxy absolute magnitude. 
Symbols are coded according to the galaxy morphological type: red circle = elliptical, red star = elliptical/lenticular, 
red upward triangle = lenticular, blue downward triangle = lenticular/spiral, blue square = spiral, black diamond = merger. 
Empty symbols represent core-S\'ersic spheroids, whereas filled symbols are used for S\'ersic spheroids. 
The red dashed line indicates the BCES bisector linear regression for early-type galaxies (ellipticals+lenticulars), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
Four spiral galaxies had their magnitudes overestimated and are shown as upper limits. }
\label{fig:mbhmaggal}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mag_sph.pdf}
\caption{Black hole mass against $3.6\rm~\mu m$ spheroid absolute magnitude. 
Symbols are coded according to the galaxy morphological type: red circle = elliptical, red star = elliptical/lenticular, 
red upward triangle = lenticular, blue downward triangle = lenticular/spiral, blue square = spiral, black diamond = merger. 
Empty symbols represent core-S\'ersic spheroids, whereas filled symbols are used for S\'ersic spheroids. 
The red dashed line indicates the BCES bisector linear regression for early-type galaxies (ellipticals+lenticulars), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The blue solid line shows the BCES bisector linear regression for spiral galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The black dashed-dotted and dotted lines represent the BCES bisector linear regressions for core-S\'ersic and S\'ersic spheroids, respectively.}
\label{fig:mbhmagsph}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mag_sph_psb.pdf}
\caption{Black hole mass versus $3.6\rm~\mu m$ spheroid absolute magnitude. 
Symbols are color coded according to the spheroid S\'ersic index $n_{\rm sph}$. 
Bulges with $n_{\rm sph}<2$, claimed by some to be pseudobulges, are marked with an empty square. 
The black solid line shows the BCES bisector linear regression for spheroids with $n_{\rm sph} \geq 2$. }
\label{fig:pseudob}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/inset_psb.pdf}
\caption{Vertical offset from the $M_{\rm BH} - L_{\rm sph}$ correlation defined by spheroids with $n_{\rm sph} \geq 2$. 
The vertical dashed line corresponds to $n_{\rm sph} = 2$.
The horizontal solid line is equivalent to a zero vertical offset.
Bulges with $n_{\rm sph}<2$ are not randomly offset to lower black hole masses 
from the correlation traced by bulges with $n_{\rm sph} \geq 2$.}
\label{fig:pseudob}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph.pdf}
\caption{Black hole mass against spheroid stellar mass. 
Symbols are coded according to the galaxy morphological type (red = E, orange = E/S0 and S0, blue = S0/Sp and Sp, black = merger).
The red dashed line indicates the BCES bisector linear regression for early-type galaxies (ellipticals+lenticulars), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The blue solid line shows the BCES bisector linear regression for spiral galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. }
\label{fig:mbhmasssph}
\end{center}
\end{figure}

@@

 Late-type (Sp) (17) & BCES $(Y|X)$      & $7.37 \pm 0.17$ & $-0.33 \pm 0.87$   & $-24.39$ & $-$ & $0.65$ \\
                     & BCES $(X|Y)$      & $7.37 \pm 1.97$ & $-21.66 \pm 53.74$ & $-24.39$ & $-$ & $7.73$ \\                        
                     & BCES Bisector     & $7.37 \pm 0.20$ & $-1.32 \pm 0.94$   & $-24.39$ & $-$ & $0.77$ \\                     
                     & FITEXY $(Y|X)$    & $7.38^{+0.17}_{-0.18}$ & $-0.34^{+0.74}_{-0.80}$ & $-24.39$ & $0.63^{+0.19}_{-0.11}$ & $0.65$ \\                         
                     & FITEXY $(X|Y)$    & $$ & $$ & $-24.39$ & $$ & $$ \\                         
                     & FITEXY Bisector   & $$ & $$ & $-24.39$ & $-$    & $$ \\                  
                     & {\tt linmix\_err} $(Y|X)$     & $$ & $$ & $-24.39$ & $$ & $$ \\             
                     & {\tt linmix\_err} $(X|Y)$     & $$ & $$ & $-24.39$ & $$ & $$ \\             
                     & {\tt linmix\_err} Bisector    & $$ & $$ & $-24.39$ & $-$    & $$ \\

@@

\tableline 
\tableline
\end{tabular}
\label{tab:lreggal} 
\end{table*}

\tableline 
\tableline
\end{tabular}
\label{tab:lregsph} 
\end{table*}

\tableline 
\tableline
\end{tabular}
\label{tab:lregmass} 
\tablecomments{cia}
\end{table*}

\subsection{Black hole mass -- galaxy luminosity}
Figure \ref{fig:mbhmaggal} illustrates the $M_{\rm BH} - L_{\rm gal}$ diagram.
Four spiral galaxies had their total luminosities underestimated (see Section \ref{sec:data}) 
and thus are not included in the linear regression analysis. \\
Upon analyzing a sample of 35 galaxies, among which only four were classified as spiral galaxies, 
\cite{lasker2014anal} claimed that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations, 
which they fit with a single power-law, have consistent intrinsic scatter.
Here, instead, thanks to our double-sized galaxy sample that includes 17 spiral galaxies, 
we show that the claim made by \cite{lasker2014anal} is valid only for early-type galaxies. 
The $M_{\rm BH} - L_{\rm sph}$ correlation for all galaxies, irrespective of their morphological type, 
has intrinsic scatter $\epsilon_{(Y|X)} = 0.51 \pm 0.06\rm~dex$ (direct linear regression) 
and $\epsilon_{(X|Y)} = 0.60 \pm 0.09\rm~dex$ (inverse linear regression), 
whereas the $M_{\rm BH} - L_{\rm gal}$ correlation for all galaxies has $\epsilon_{(Y|X)} = 0.63 \pm 0.07\rm~dex$ 
and $\epsilon_{(X|Y)} = 0.91 \pm 0.17\rm~dex$.
However, when considering only early-type galaxies, 
we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations have the same level of intrinsic scatter. 
%($\epsilon_{(Y|X)} = 0.41 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.51 \pm 0.10\rm~dex$ 
%against $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.53 \pm 0.10\rm~dex$).
Because the value of the intrinsic scatter depends on the uncertainties associated to the luminosities\footnote{The 
smaller (larger) the uncertainties, the larger (smaller) the intrinsic scatter.}, 
we tested the robustness of our last conclusion by increasing/decreasing the errors associated to $L_{\rm gal}$ 
(that we originally assumed to be $0.25\rm~mag$) and repeating the linear regression analysis. 
On the other hand, the uncertainties associated to $L_{\rm sph}$ have been estimated 
with an advanced method that takes into account the systematic errors related to the galaxy decomposition process. 
We consider these uncertainties trustworthy and, therefore, we decided to vary only the errors associated to $L_{\rm gal}$.
We found that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations for early-type galaxies 
have inconsistent intrinsic scatter when assuming an error $\geq 0.7\rm~mag$ on $L_{\rm gal}$. 
Because such error is larger than the typical error on $L_{\rm sph}$ used here
-- and, in general, is significantly larger than the uncertainties on $L_{\rm gal}$ that are typically used in the literature --, 
we come to the conclusion that our determination of the intrinsic scatter is reliable, 
and that, for early-type galaxies, $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$.
As \cite{lasker2014anal} pointed out, from the observer's perspective, measuring galaxy luminosities is obviously easier and faster 
than performing accurate %galaxy decompositions to obtain bulge luminosities. 
This, combined with our last conclusion, suggests that one should prefer the galaxy luminosity over the bulge luminosity 
to predict black hole masses when dealing with samples of elliptical and lenticular galaxies only.

@@

We show the $M_{\rm BH} - L_{\rm sph}$ diagram in Figure \ref{fig:mbhmagsph}. \\

@@

The slope that we obtained for core-S\'ersic spheroids ($M_{\rm BH} \propto L_{\rm sph}^{1.2 \pm 0.2}$) 
is consistent with the slope reported by GS13 in the $K_s$-band ($M_{\rm BH} \propto L_{\rm sph}^{1.1 \pm 0.2}$). 
Instead, the slope that we determined for S\'ersic spheroids ($M_{\rm BH} \propto L_{\rm sph}^{1.5 \pm 0.2}$) 
is significantly shallower than that found by GS13 ($M_{\rm BH} \propto L_{\rm sph}^{2.7 \pm 0.5}$). 

@@

while the bulge-to-total ratios of GS13 were derived from simple bulge/disk decompositions 

@@

This results in our bulge magnitudes being on average $\sim$$1\rm~mag$ fainter.

@@

In this case, the host systems are early-type elliptical/lenticular galaxies that feature intermediate-scale disks\footnote{explain}.

@@

The magnitudes that we obtained for such spheroids are on average $\sim$$1\rm~mag$ brighter. \\

@@

the spheroids of early-type (elliptical and lenticular) galaxies will follow $M_{\rm BH} \propto L_{\rm sph}^{\sim 1}$, 
whereas the spheroids of late-type (spiral) galaxies will have $M_{\rm BH} \propto L_{\rm sph}^{\sim 2.5}$.

@@

and obtained $M_{\rm BH} \propto L_{\rm sph}^{1 \pm 0.1}$ and $M_{\rm BH} \propto L_{\rm sph}^{2.75 \pm 0.75}$ respectively, 
in excellent agreement with the theoretical expectations of our hypothesis.

@@

{\bf AL, can you pls write this: 
Remember also Ewan's remark about the unsuitability of the Pearson and Spearman correlation coefficients because 
they do not take into account the error bars on our data - 
so don't include those simple coefficients.  
Actually, it would be worth pointing out to readers that a visual inspection of the plotted data requires 
the viewer to take into account the error bars when judging-by-eye the strength of a correlation. 
Maybe then mention in the following sentence that this is why the correlation coefficients are not applicable here. }

\subsection{Pseudo- versus classical bulges}
Current views distinguish between classical bulges, which are considered to be spheroidal, pressure-supported systems, 
formed through violent processes, such as hierarchical clustering via minor mergers, 
and pseudo-bulges, thought to be disk-like, rotation-supported systems, 
built from secular evolution processes, such as instabilities of their surrounding disk or bar. 
Pseudo-bulges are notoriously hard to identify \citep{graham2013review,graham2014review,graham2015pseudo,graham2015review}.
For example, mergers can create bulges that rotate (e.g.~\citealt{bekki2010,keselmannusser2012}), 
and bars can spin-up classical bulges (e.g.~\citealt{saha2012}), 
thus rotation is not a definitive signature of a pseudobulge. 
Furthermore, many galaxies host both a pseudo- and a classical bulge (e.g.~\citealt{erwin2003,erwin2015,athanassoula2005,Gadotti2009,
macarthur2009,dosanjosdasilva2013,seidel2015}). 
In the recent literature, pseudo- and classical bulges have been frequently told apart by means of a divide at a 
S\'ersic index of $n_{\rm sph}=2$ (e.g.~\citealt{fisherdrory2010}), 
although, from a selection of hundreds of disc galaxies imaged in the $K$-band, 
\cite{grahamworley2008} observed no such bimodality in the bulge S\'ersic indices. 
While pseudo-bulges are expected to have exponential-like surface brightness profiles ($n_{\rm sph} \simeq 1$), 
being disky components that formed from their surrounding exponential disks 
(e.g.~\citealt{bardeen1975,hohl1975,combessanders1981,combes1990,pfennigerfriedli1991}), 
it has been shown that mergers can create bulges with $n_{\rm sph}<2$
(e.g.~\citealt{elichemoral2011,scannapieco2011,querejeta2015}), 
just as low-luminosity elliptical galaxies (not built from the secular evolution of a disk)
are well known to have $n_{\rm sph}<2$ and even $n_{\rm sph}<1$ (e.g.~\citealt{davies1988,youngcurrie1994}). \\
\cite{sani2011} reported that pseudo-bulges -- which they labelled as such according to the $n_{\rm sph}<2$ criterion -- 
with low black hole masses ($M_{\rm BH} < 10^7\rm~M_\odot$) are significantly displaced from the correlation 
traced by classical bulges. 
In Figure \ref{fig:pseudob}, we show the distribution of spheroid S\'ersic indices\footnote{The spheroid S\'ersic indices 
are taken from our one-dimensional fits of the galaxy major-axis surface brightness profiles (\emph{Paper I}).} 
in the $M_{\rm BH} - L_{\rm sph}$ diagram.
Our aim is to check whether $n_{\rm sph}<2$ bulges 
are offset to lower black hole masses from the correlation defined by $n_{\rm sph}>2$ bulges. 
To do this, we fit a symmetrical linear regression to the bulges that have $n_{\rm sph}>2$ 
and we compute the vertical offset of all bulges from the regression. 
In the inset of Figure \ref{fig:pseudob}, we plot the vertical offset against $n_{\rm sph}$. 
From a visual inspection, bulges with $n_{\rm sph}<2$ do not appear to be offset from the correlation traced by bulges with $n_{\rm sph}>2$.

\subsection{Black hole mass -- spheroid stellar mass}
Finally, we present the $M_{\rm BH} - M_{\rm *,sph}$ diagram in Figure \ref{fig:mbhmasssph}. 
The bulges of early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.0 \pm 0.1}$,
as expected from a dry-merging formation scenario,
and define a tight \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 
On the other hand, the bulges of spiral galaxies trace a steeper \emph{blue sequence}, 
whose slope is not well constrained due to the small size of the subsample and, more importantly, 
to the small range in $M_{\rm *,sph}$ that the subsample spans.
For the bulges of spiral galaxies, the BCES code returns a bisector linear regression $M_{\rm BH} \propto M_{\rm *,sph}^{3.0 \pm 1.3}$, 
while the modified FITEXY routine finds a shallower (but still consistent within the $1\sigma$ uncertainty) slope of $2.3^{+1.7}_{-1.0}$.
The Bayesian estimator of \cite{linmixerr} fails in performing an inverse $(X|Y)$ linear regression for the subsample of spiral galaxies. 
{\bf which code do we trust more in this case? BCES or FITEXY? is it a quadratic or a cubic growth? }

\cite{grahamscott2015} collected a sample of $\sim$170 low-redshift ($z \lesssim 0.1$) bulges hosting Active Galactic Nuclei (AGNs) with 
black hole masses $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 0.5 \times 10^8$, 
and showed that they roughly follow the quadratic $M_{\rm BH} - M_{\rm *,sph}$ relation defined by predominantly inactive S\'ersic bulges. 
Although we demonstrated that, using our dataset, the S\'ersic bulges do not define a quadratic relation, 
we anticipate here that the correlation traced by our bulges of spiral galaxies 
tracks the location of the AGNs in the $M_{\rm BH} - M_{\rm *,sph}$ diagram, 
i.e. the AGNs appears to be the low-mass continuation of the \emph{blue sequence} shown in Figure \ref{fig:mbhmasssph}. 
We also note that the majority of our spiral galaxies hosts an AGN\footnote{According to the nuclear classification reported on NED 
(Nasa Extragalactic Database), among our 17 spiral galaxies, at least 12 host a Seyfert AGN and one hosts a LINER AGN.}.\\
{\bf cite Anne's paper}\\
{\bf AL: however we analyze the agns in another paper, blah blah}

>>>>

Following GS13, we assumed a fixed uncertainty ($0.25\rm~mag$) for $MAG_{\rm gal}$. \\
The morphological classification (E = elliptical; E/S0 = elliptical/lenticular; S0 = lenticular; S0/Sp = lenticular/spiral; Sp = spiral; merger) 
follows from the galaxy models presented in \emph{Paper I}. 
Throughout the paper, we will refer to early-type galaxies (E+S0) and late-type galaxies (Sp). 
Galaxies classified as E/S0 are obviously included in the early-type bin, 
whereas galaxies classified as S0/Sp or as mergers are included in neither the early- nor the late-type bin.\\

@@

comes from the compilation of \citet{savorgnangraham2015},

@@

@@

\subsection{Black hole mass -- galaxy luminosity}
Figure \ref{fig:mbhmaggal} illustrates the $M_{\rm BH} - L_{\rm gal}$ diagram.
Four spiral galaxies had their total luminosities underestimated (see Section \ref{sec:data}) 
and thus are not included in the linear regression analysis (see Table \ref{tab:lreggal}). \\
Upon analyzing a sample of 35 galaxies, among which only four were classified as spiral galaxies, 
\cite{lasker2014anal} claimed that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations, 
which they fit with a single power-law, have consistent intrinsic scatter.
Here, instead, thanks to our double-sized galaxy sample that includes 17 spiral galaxies, 
we show that the claim made by \cite{lasker2014anal} is valid only for early-type galaxies. 
The $M_{\rm BH} - L_{\rm sph}$ correlation for all galaxies, irrespective of their morphological type, 
has intrinsic scatter $\epsilon_{(Y|X)} = 0.51 \pm 0.06\rm~dex$ (direct linear regression) 
and $\epsilon_{(X|Y)} = 0.60 \pm 0.09\rm~dex$ (inverse linear regression), 
whereas the $M_{\rm BH} - L_{\rm gal}$ correlation for all galaxies has $\epsilon_{(Y|X)} = 0.63 \pm 0.07\rm~dex$ 
and $\epsilon_{(X|Y)} = 0.91 \pm 0.17\rm~dex$.
However, when considering only early-type galaxies, 
we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations have the same level of intrinsic scatter. 
%($\epsilon_{(Y|X)} = 0.41 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.51 \pm 0.10\rm~dex$ 
%against $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.53 \pm 0.10\rm~dex$).
Because the value of the intrinsic scatter depends on the uncertainties associated to the luminosities\footnote{The 
smaller (larger) the uncertainties, the larger (smaller) the intrinsic scatter.}, 
we tested the robustness of our last conclusion by increasing/decreasing the errors associated to $L_{\rm gal}$ 
(that we originally assumed to be $0.25\rm~mag$) and repeating the linear regression analysis. 
We decided to vary only the errors associated to $L_{\rm gal}$ 
because we consider the uncertainties associated to $L_{\rm sph}$ trustworthy, since they have been estimated with an advanced method 
that takes into account the systematic errors related to the galaxy decomposition process. 
We found that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations for early-type galaxies 
have inconsistent intrinsic scatter when assuming an error $\geq 0.7\rm~mag$ on $L_{\rm gal}$. 
Because such error is larger than the typical error on $L_{\rm sph}$ estimated by us 
and, in general, is significantly larger than the uncertainties on $L_{\rm gal}$ that are typically assumed in the literature, 
we conclude that our determination of the intrinsic scatter is reliable, 
and that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, but not for all (early+late) galaxies.
As \cite{lasker2014anal} pointed out, from the observer's perspective, measuring galaxy luminosities is obviously easier and faster 
than performing accurate galaxy decompositions to obtain bulge luminosities. 
This, combined with our last conclusion, suggests that one should prefer the galaxy luminosity over the bulge luminosity 
to predict black hole masses when dealing with samples of elliptical and lenticular galaxies only.

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mag_tot.pdf}
\caption{Black hole mass plotted against $3.6\rm~\mu m$ galaxy absolute magnitude. 
Symbols are coded according to the galaxy morphological type: red circle = E, red star = E/S0, 
red upward triangle = S0, blue downward triangle = S0/Sp, blue square = Sp, black diamond = merger. 
Empty symbols represent core-S\'ersic spheroids, whereas filled symbols are used for S\'ersic spheroids. 
Four spiral galaxies had their magnitudes overestimated and are shown as upper limits. 
The red dashed line indicates the BCES bisector linear regression for 45 early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
We were not able to obtain any meaningful linear regression for the late-type (Sp) galaxies. }
\label{fig:mbhmaggal}
\end{center}
\end{figure}

@@

%Late-type (Sp) (13) & BCES $(Y|X)$      & $7.37 \pm 0.17$ & $-0.33 \pm 0.87$   & $-24.39$ & $-$ & $0.65$ \\
%                    & BCES $(X|Y)$      & $7.37 \pm 1.97$ & $-21.66 \pm 53.74$ & $-24.39$ & $-$ & $7.73$ \\
%                    & BCES Bisector     & $7.37 \pm 0.20$ & $-1.32 \pm 0.94$   & $-24.39$ & $-$ & $0.77$ \\
%                    & FITEXY $(Y|X)$    & $7.38^{+0.17}_{-0.18}$ & $-0.34^{+0.74}_{-0.80}$ & $-24.39$ & $0.63^{+0.19}_{-0.11}$ & $0.65$ \\
%                    & FITEXY $(X|Y)$    & $$ & $$ & $-24.39$ & $$ & $$ \\
%                    & FITEXY Bisector   & $$ & $$ & $-24.39$ & $-$    & $$ \\
%                    & {\tt linmix\_err} $(Y|X)$     & $$ & $$ & $-24.39$ & $$ & $$ \\
%                    & {\tt linmix\_err} $(X|Y)$     & $$ & $$ & $-24.39$ & $$ & $$ \\
%                    & {\tt linmix\_err} Bisector    & $$ & $$ & $-24.39$ & $-$    & $$ \\

@@

\tableline 
\tableline
\end{tabular}
\label{tab:lreggal} 
\tablecomments{For each subsample, we indicate $\langle MAG_{\rm gal} \rangle$, its average value of galaxy magnitudes. 
In the last two columns, we report $\epsilon$, the intrinsic scatter, and $\Delta$, the total rms scatter in the $\log(M_{\rm BH})$ direction. 
Four spiral galaxies had their luminosities underestimated and thus are not included in the linear regression analysis 
(the sample of all galaxies contains 66-4=62 objects). 
When considering all galaxies, irrespective of their morphological type, 
the $M_{\rm BH} - L_{\rm gal}$ correlation is weaker than the $M_{\rm BH} - L_{\rm sph}$ correlation, in terms of intrinsic scatter. 
However, when considering only early-type galaxies, the $M_{\rm BH} - L_{\rm gal}$ and $M_{\rm BH} - L_{\rm sph}$ correlations 
have consistent intrinsic scatter. }
\end{table*}

@@

We now come to the $M_{\rm BH} - L_{\rm sph}$ diagram, which is shown in Figure \ref{fig:mbhmagsph}, 
and whose linear regression analysis is presented in Table \ref{tab:lregsph}. \\

@@

The slope that we obtained for core-S\'ersic spheroids ($M_{\rm BH} \propto L_{\rm sph}^{1.18 \pm 0.20}$) 
is consistent with the slope reported by GS13 in the $K_s$-band ($M_{\rm BH} \propto L_{\rm sph}^{1.10 \pm 0.20}$). 
Instead, the slope that we determined for S\'ersic spheroids ($M_{\rm BH} \propto L_{\rm sph}^{1.53 \pm 0.20}$) 
is shallower than that found by GS13 ($M_{\rm BH} \propto L_{\rm sph}^{2.73 \pm 0.55}$). 

@@

while the bulge-to-total ratios of GS13 were derived from simple literature bulge/disk decompositions 

@@

This results in our bulge magnitudes being on average $\sim$$1\rm~mag$ fainter than in GS13, after accounting for the different wavelength of the data.

@@

In this case, the host systems are early-type galaxies that feature intermediate-scale disks\footnote{explain}.

@@

The magnitudes that we obtained for such spheroids are on average $\sim$$1\rm~mag$ brighter than in GS13. 
These two effects explain the shallower slope that we obtained for the S\'ersic spheroids. \\

@@

the spheroids of early-type galaxies will follow $M_{\rm BH} \propto L_{\rm sph}^{\sim 1}$, 
whereas the spheroids of late-type galaxies will have $M_{\rm BH} \propto L_{\rm sph}^{\sim 2.5}$.

@@

and obtained $M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$ and $M_{\rm BH} \propto L_{\rm sph}^{2.75 \pm 0.75}$ respectively, 
in excellent agreement with the theoretical expectations of our hypothesis. \\

@@

We remark on the unsuitability of the Pearson's and Spearman's correlation coefficients because 
they do not take into account the error bars on our data.
Similarly, a visual inspection of the plotted data requires us to take into account the error bars 
when judging-by-eye the strength of a correlation. 
We have therefore relied on the quantitative regression analysis rather than subjective approaches.

\subsection{Pseudo- versus classical bulges}
korm. review \\
Current views distinguish between classical bulges, which are considered to be spheroidal, pressure-supported systems, 
formed through violent processes, such as hierarchical clustering via minor mergers, 
and pseudo-bulges, thought to be disk-like, rotation-supported systems, 
built from secular evolution processes, such as instabilities of their surrounding disk or bar. 
Pseudo-bulges are notoriously hard to identify \citep{graham2013review,graham2014review,graham2015pseudo,graham2015review}.
For example, mergers can create bulges that rotate (e.g.~\citealt{bekki2010,keselmannusser2012}), 
and bars can spin-up classical bulges (e.g.~\citealt{saha2012}), 
thus rotation is not a definitive signature of a pseudobulge. 
Furthermore, many galaxies host both a pseudo- and a classical bulge (e.g.~\citealt{erwin2003,erwin2015,athanassoula2005,Gadotti2009,
macarthur2009,dosanjosdasilva2013,seidel2015}). 
In the recent literature, pseudo- and classical bulges have been frequently told apart by means of a divide at a 
S\'ersic index of $n_{\rm sph}=2$ (e.g.~\citealt{fisherdrory2010}), 
although, from a selection of hundreds of disc galaxies imaged in the $K$-band, 
\cite{grahamworley2008} observed no such bimodality in the bulge S\'ersic indices. 
While pseudo-bulges are expected to have exponential-like surface brightness profiles ($n_{\rm sph} \simeq 1$), 
being disky components that formed from their surrounding exponential disks 
(e.g.~\citealt{bardeen1975,hohl1975,combessanders1981,combes1990,pfennigerfriedli1991}), 
it has been shown that mergers can create bulges with $n_{\rm sph}<2$
(e.g.~\citealt{elichemoral2011,scannapieco2011,querejeta2015}), 
just as low-luminosity elliptical galaxies (not built from the secular evolution of a disk)
are well known to have $n_{\rm sph}<2$ and even $n_{\rm sph}<1$ (e.g.~\citealt{davies1988,youngcurrie1994}). \\
\cite{sani2011} reported that pseudo-bulges -- which they labelled as such according to the $n_{\rm sph}<2$ criterion -- 
with low black hole masses ($M_{\rm BH} < 10^7\rm~M_\odot$) are significantly displaced from the correlation 
traced by classical bulges. 
In Figure \ref{fig:pseudob}, we show the distribution of spheroid S\'ersic indices\footnote{The spheroid S\'ersic indices 
are taken from our one-dimensional fits of the galaxy major-axis surface brightness profiles (\emph{Paper I}).} 
in the $M_{\rm BH} - L_{\rm sph}$ diagram.
Our aim is to check whether $n_{\rm sph}<2$ bulges 
are offset to lower black hole masses from the correlation defined by $n_{\rm sph}>2$ bulges. 
To do this, we fit a symmetrical linear regression to the bulges that have $n_{\rm sph}>2$ 
and we compute the vertical offset of all bulges from the regression. 
In the inset of Figure \ref{fig:pseudob}, we plot the vertical offset against $n_{\rm sph}$. 
From a visual inspection, bulges with $n_{\rm sph}<2$ do not appear to be offset from the correlation traced by bulges with $n_{\rm sph}>2$.

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mag_sph.pdf}
\caption{Black hole mass plotted against $3.6\rm~\mu m$ spheroid absolute magnitude. 
Symbols are coded according to the galaxy morphological type: red circle = E, red star = E/S0, 
red upward triangle = S0, blue downward triangle = S0/Sp, blue square = Sp, black diamond = merger. 
Empty symbols represent core-S\'ersic spheroids, whereas filled symbols are used for S\'ersic spheroids. 
The red dashed line indicates the BCES bisector linear regression for the bulges of 45 early-type (E+S0) galaxies, 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The blue solid line shows the BCES bisector linear regression for the bulges of 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The black dashed-dotted and dotted lines represent the BCES bisector linear regressions for core-S\'ersic and S\'ersic spheroids, respectively.}
\label{fig:mbhmagsph}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mag_sph_psb.pdf}
\caption{Black hole mass plotted against $3.6\rm~\mu m$ spheroid absolute magnitude. 
Symbols are color coded according to the spheroid S\'ersic index $n_{\rm sph}$. 
Bulges with $n_{\rm sph}<2$, claimed by some to be pseudobulges, are marked with an empty square. 
The black solid line shows the BCES bisector linear regression for spheroids with $n_{\rm sph} \geq 2$. }
\label{fig:pseudob}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/inset_psb.pdf}
\caption{Vertical offset from the $M_{\rm BH} - L_{\rm sph}$ correlation defined by spheroids with $n_{\rm sph} \geq 2$, 
plotted against $n_{\rm sph}$. 
The vertical dashed line corresponds to $n_{\rm sph} = 2$.
The horizontal solid line is equivalent to a zero vertical offset.
Bulges with $n_{\rm sph}<2$ are not randomly offset to lower black hole masses 
from the correlation traced by bulges with $n_{\rm sph} \geq 2$.}
\label{fig:pseudob}
\end{center}
\end{figure}

\tableline 
\tableline
\end{tabular}
\label{tab:lregsph} 
\tablecomments{For each subsample, we indicate $\langle MAG_{\rm sph} \rangle$, its average value of spheroid magnitudes. 
In the last two columns, we report $\epsilon$, the intrinsic scatter, and $\Delta$, the total rms scatter in the $\log(M_{\rm BH})$ direction. 
Both the early- and late-type subsamples do not contain the two galaxies classified as S0/Sp and the two galaxies classified as mergers (45+17=66-2-2). }
\end{table*}

\subsection{Black hole mass -- spheroid stellar mass}
Finally, we present the $M_{\rm BH} - M_{\rm *,sph}$ diagram in Figure \ref{fig:mbhmasssph}. 
The bulges of early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.0 \pm 0.1}$,
as expected from a dry-merging formation scenario,
and define a tight \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 
On the other hand, the bulges of spiral galaxies trace a steeper \emph{blue sequence}, 
whose slope is less well constrained due to the small size of the subsample and, more importantly, 
to the small range in $M_{\rm *,sph}$ that the subsample spans.
For the bulges of spiral galaxies, the BCES code returns a bisector linear regression $M_{\rm BH} \propto M_{\rm *,sph}^{3.0 \pm 1.3}$, 
while the modified FITEXY routine finds a shallower (but still consistent within the $1\sigma$ uncertainty) slope of $2.3^{+1.7}_{-1.0}$.
The Bayesian estimator of \cite{linmixerr} fails in performing an inverse $(X|Y)$ linear regression for the subsample of spiral galaxies. 
{\bf which code do we trust more in this case? BCES or FITEXY? is it a quadratic or a cubic growth? }

\cite{grahamscott2015} collected a sample of $\sim$170 low-redshift ($z \leq 0.35$, with a median redshift $\langle z \rangle = 0.085$) 
bulges hosting Active Galactic Nuclei (AGNs) with 
black hole masses $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 0.5 \times 10^8$, 
and showed that they roughly follow the quadratic $M_{\rm BH} - M_{\rm *,sph}$ relation defined by predominantly inactive S\'ersic bulges. 
%Although we demonstrated that, using our dataset, the S\'ersic bulges do not define a quadratic relation, 
We anticipate here that the correlation traced by our bulges of spiral galaxies 
may track the location of the AGNs in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.
That is, the AGNs appear to be the low-mass continuation of the \emph{blue sequence} shown in Figure \ref{fig:mbhmasssph}. 
We additionally note that the majority of our spiral galaxies host an AGN\footnote{According to the nuclear classification reported on NED 
(Nasa Extragalactic Database), among our 17 spiral galaxies, at least 12 host a Seyfert AGN and one hosts a LINER AGN.}.\\
{\bf cite Anne's paper}\\
{\bf AL: however we analyze the agns in another paper, blah blah}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph.pdf}
\caption{Black hole mass plotted against spheroid stellar mass. 
Symbols are coded according to the galaxy morphological type.
The red dashed line indicates the BCES bisector linear regression for early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The blue solid line shows the BCES bisector linear regression for late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. {\bf key result}}
\label{fig:mbhmasssph}
\end{center}
\end{figure}
